Block bootstrap consistency\\under weak assumptions

### 2017-02-06 Paper.tex
[#40/check] Spellcheck documents

\begin{lem}\label{L3}
Under the conditions of Theorem~\ref{T1},
\begin{equation}\label{eq:40}
  \E \Big(\sum_{j=1}^{J_n} \Big( \sum_{t = K_{n,j-1}+1}^{K_{nj}}
  (\mu_{nt}^{*} - \bar \mu_n)\Big)^2\Big) = o(n p_n)
\end{equation}
and $\bar \mu_n^{*} = \E^{*} \bar \mu_n^{*} + o_{L_2}(n^{-1/2})$.
\end{lem}
\begin{proof}
  The second result, on $\bar\mu_n^*$, is an immediate implication of
  Equation~\eqref{eq:40}. To show~\eqref{eq:40}, observe that
  \begin{align*}
    \E \Big(\sum_{j=1}^{J_n} &\Big( \sum_{t= K_{n,j-1} +1}^{K_{nj}}
    (\mu_{nt}^{*} - \bar \mu_n)\Big)^2\Big)= \\
    &= \E\Big(\sum_{j=1}^{J_n} \big\lvert \sum_{s,t = K_{n,j-1}+1}^{K_{nj}}
    \E \big((\mu_{ns}^{*} - \bar{\mu}_n)
    (\mu_{nt}^{*} - \bar{\mu}_n) \mid \Ms \big) \big\rvert \Big)\\
    &\leq \E\Big( \sum_{j=1}^{J_n}
    \sum_{k,l = -n}^{n} \tfrac{1}{n} \sum_{\tau=0}^{n-1} \big\lvert
    (\mu_{n,\tau+k} - \bar{\mu}_n) (\mu_{n,\tau+l} - \bar{\mu}_n) \;
    1\{ \tau + k, \tau + l \in I_n(\tau, M_{nj})\} \big\rvert \Big)\\
    &\leq \E\Big(\sum_{j=1}^{J_n} \Big[
    \sum_{k = -n}^{n} \big(\tfrac{1}{n} \sum_{\tau=0}^{n-1}
    (\mu_{n,\tau+k} - \bar{\mu}_n)^2
    1\{ \tau + k \in I_n(\tau, M_{nj})\}\big)^{1/2}\Big]^{2}\Big)\\
    &= \E\Big(\sum_{j=1}^{J_n}
    M_{nj}^2 \Big\lvert \tfrac{1}{n} \sum_{\tau=0}^{n-1}
    (\mu_{n,\tau} - \bar{\mu}_n)^2 \Big\lvert\Big)\\
    &= o(n p_n).
  \end{align*}
  The first equality follows from the LIE\@. The first inequality
  exploits the fact that the conditional expectation in the previous
  expression averages over the block's starting period but treats
  every other random variable as contstant. (The argument of the
  indicator function and the indices of the summations are
  deliberately chosen to accomodate blocks that include observations
  from both the beginning and the end of the series.) The second
  inequality is an application of the Cauchy-Schwarz inequality to the
  inner-most summation. The next equality holds because the
  summation
  \[
    \sum_{\tau=0}^{n-1} (\mu_{n,\tau+k} - \bar{\mu}_n)^2
    1\{ \tau + k \in I_n(\tau, M_{nj})\}
  \]
  is zero for all but $M_{nj}$ values of $k$ and is a nonzero constant
  for those $k$. The last line holds by Lemma~\ref{L1} and assumption.
\end{proof}

>>>>

\begin{lem}\label{L3}
Under the conditions of Theorem~\ref{T1},
\begin{equation}\label{eq:40}
  \E \Big(\sum_{j=1}^{J_n} \Big( \sum_{t = K_{n,j-1}+1}^{K_{nj}}
  (\mu_{nt}^{*} - \bar \mu_n)\Big)^2\Big) = o(n p_n)
\end{equation}
and $\bar \mu_n^{*} = \E^{*} \bar \mu_n^{*} + o_{L_2}(n^{-1/2})$.
\end{lem}
\begin{proof}
  The second result, on $\bar\mu_n^*$, is an immediate implication of
  Equation~\eqref{eq:40}. To show~\eqref{eq:40}, observe that
  \begin{align*}
    \E \Big(\sum_{j=1}^{J_n} &\Big( \sum_{t= K_{n,j-1} +1}^{K_{nj}}
    (\mu_{nt}^{*} - \bar \mu_n)\Big)^2\Big)= \\
    &= \E\Big(\sum_{j=1}^{J_n} \big\lvert \sum_{s,t = K_{n,j-1}+1}^{K_{nj}}
    \E \big((\mu_{ns}^{*} - \bar{\mu}_n)
    (\mu_{nt}^{*} - \bar{\mu}_n) \mid \Ms \big) \big\rvert \Big)\\
    &\leq \E\Big( \sum_{j=1}^{J_n}
    \sum_{k,l = -n}^{n} \tfrac{1}{n} \sum_{\tau=0}^{n-1} \big\lvert
    (\mu_{n,\tau+k} - \bar{\mu}_n) (\mu_{n,\tau+l} - \bar{\mu}_n) \;
    1\{ \tau + k, \tau + l \in I_n(\tau, M_{nj})\} \big\rvert \Big)\\
    &\leq \E\Big(\sum_{j=1}^{J_n} \Big[
    \sum_{k = -n}^{n} \big(\tfrac{1}{n} \sum_{\tau=0}^{n-1}
    (\mu_{n,\tau+k} - \bar{\mu}_n)^2
    1\{ \tau + k \in I_n(\tau, M_{nj})\}\big)^{1/2}\Big]^{2}\Big)\\
    &= \E\Big(\sum_{j=1}^{J_n}
    M_{nj}^2 \Big\lvert \tfrac{1}{n} \sum_{\tau=0}^{n-1}
    (\mu_{n,\tau} - \bar{\mu}_n)^2 \Big\lvert\Big)\\
    &= o(n p_n).
  \end{align*}
  The first equality follows from the LIE\@. The first inequality
  exploits the fact that the conditional expectation in the previous
  expression averages over the block's starting period but treats
  every other random variable as constant. (The argument of the
  indicator function and the indices of the summations are
  deliberately chosen to accommodate blocks that include observations
  from both the beginning and the end of the series.) The second
  inequality is an application of the Cauchy-Schwarz inequality to the
  inner-most summation. The next equality holds because the
  summation
  \[
    \sum_{\tau=0}^{n-1} (\mu_{n,\tau+k} - \bar{\mu}_n)^2
    1\{ \tau + k \in I_n(\tau, M_{nj})\}
  \]
  is zero for all but $M_{nj}$ values of $k$ and is a nonzero constant
  for those $k$. The last line holds by Lemma~\ref{L1} and assumption.
\end{proof}
